\documentclass[11pt,a4paper]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{xcolor} % Fixed: Added for \color support

% Document Margins
\geometry{left=0.6in, top=0.5in, right=0.6in, bottom=0.5in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Fix for footskip warning
\setlength{\footskip}{4.1pt}

% Section formatting - Minimal & ATS Friendly
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge \textbf{Alisina Karimi}} \\ \vspace{4pt}
    \small Turin, Italy $|$ \href{mailto:alisinakarimi.2003@gmail.com}{\underline{alisinakarimi.2003@gmail.com}} \\
    \href{https://alisinadevelo.github.io}{\underline{Portfolio}} $|$ 
    \href{https://github.com/AliSinaDevelo}{\underline{GitHub}} $|$ 
    \href{https://linkedin.com/in/alisina-karimi}{\underline{LinkedIn}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Software Engineer specializing in scalable systems and distributed architectures. B.Sc. in Computer Engineering with a track record of optimizing production systems, reducing infrastructure costs via architectural improvements, and building end-to-end analytics platforms. Experienced in high-autonomy remote environments across multiple time zones.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {WineHub Commerce}{Nov 2024 -- Present}
      {Full Stack / Backend Engineer}{Adelaide, Australia (Remote)}
      \resumeItemListStart
        \resumeItem{Optimized database queries and performance, achieving \textbf{3×--10× improvements} across critical workloads.}
        \resumeItem{Worked on migration from MariaDB to \textbf{PostgreSQL}, resulting in a \textbf{~60\% infrastructure cost reduction}.}
        \resumeItem{Designed and implemented \textbf{Go-based microservices} for analytics, billing, and webhook processing.}
        \resumeItem{Built a full BI platform (custom dashboards, reporting pipelines) for financial decision-making.}
        \resumeItem{Integrated compliance/fulfillment APIs: Sovos ShipCompliant, Avalara, VinoShipper, and WineDirect.}
        \resumeItem{Automated reporting and compliance pipelines, significantly reducing operational overhead.}
      \resumeItemListEnd

 \resumeSubheading
  {Moneyviz srl}{May 2024 -- Nov 2024}
  {Full Stack Developer}{Turin, Italy}
  \resumeItemListStart
    \resumeItem{Developed financial analytics features using \textbf{Laravel} and \textbf{Vue.js}, enabling portfolio performance tracking and visualization for end users.}
    \resumeItem{Improved backend data ingestion and transformation pipelines, reducing latency of analytical queries and improving responsiveness of dashboards.}
    \resumeItem{Refactored data processing logic to improve consistency across financial reporting workflows and reduce edge-case discrepancies.}
    \resumeItem{Collaborated closely with product stakeholders to translate financial requirements into scalable backend and UI implementations.}
  \resumeItemListEnd

\resumeSubheading
  {RUN Polito APS-ETS}{Sep 2022 -- May 2024}
  {Software Developer}{Turin, Italy}
  \resumeItemListStart
    \resumeItem{Developed internal tools using \textbf{Go} and \textbf{JavaScript} to support operational workflows for a multi-team student organization.}
    \resumeItem{Automated administrative and coordination processes, reducing manual workload and improving turnaround time for internal requests.}
    \resumeItem{Refactored legacy services to improve maintainability and reliability, reducing recurring issues and simplifying future feature development.}
    \resumeItem{Worked directly with non-technical stakeholders to identify inefficiencies and design practical software solutions.}
  \resumeItemListEnd

\resumeSubheading
  {WEEEOpen}{May 2022 -- Aug 2022}
  {Back-end Developer}{Turin, Italy}
  \resumeItemListStart
    \resumeItem{Improved backend services using \textbf{Django}, enhancing performance and stability of core application features.}
    \resumeItem{Supported frontend integration using \textbf{React}, improving data flow between backend APIs and user interfaces.}
    \resumeItem{Participated in debugging and issue resolution across the stack, reducing friction in development and testing cycles.}
  \resumeItemListEnd

\resumeSubheading
  {Open Source / Freelance Developer}{Sep 2021 -- Present}
  {Software Developer}{Remote}
  \resumeItemListStart
    \resumeItem{Designed and implemented distributed data processing prototypes using \textbf{Kafka} and \textbf{Node.js} for event-driven workflows.}
    \resumeItem{Contributed to open-source backend projects, focusing on API design, documentation, and developer experience improvements.}
    \resumeItem{Worked independently on multiple small-scale projects, strengthening ability to scope, design, and deliver features end-to-end.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Chatster} $|$ \emph{Go, React, SQLite, Gorilla WebSocket, Prometheus, Docker, GitHub Actions}}{}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{real-time chat} reference stack: WebSocket hub with buffered broadcast, \textbf{per-client write serialization} for safe concurrent use of Gorilla WebSocket, and \textbf{SQLite}-backed history with configurable replay of recent messages on connect.}
            \resumeItem{Shipped operator-facing endpoints: structured \textbf{JSON logging} (\texttt{slog}), \textbf{graceful shutdown}, \texttt{/health} with database ping (degraded \texttt{503}), and \texttt{/metrics} for \textbf{Prometheus}.}
            \resumeItem{Added \textbf{abuse controls}: maximum username/message sizes, \textbf{per-IP WebSocket upgrade rate limiting}, and optional \textbf{Origin} allowlist for production hardening.}
            \resumeItem{Automated quality with \textbf{GitHub Actions} (Go tests with race detector, coverage, \textbf{ESLint} on the React SPA), \textbf{Docker Compose} for local full-stack runs, and portfolio-grade architecture, threat-model, and scaling documentation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Quorabust} $|$ \emph{Python, XGBoost, scikit-learn, HTTP API, Prometheus, Docker, pytest}}{}
          \resumeItemListStart
            \resumeItem{Built an installable \textbf{Python} library for \textbf{Quora-style duplicate question detection}: text cleaning, pairwise \textbf{TF--IDF} and lexical features, \textbf{XGBoost} classifier, and optional \textbf{embedding}-based feature backends.}
            \resumeItem{Delivered \textbf{train and serve CLIs} plus an HTTP service exposing prediction, \textbf{Prometheus} metrics at \texttt{/metrics}, interactive \textbf{API documentation}, and optional \textbf{A/B} model selection via request headers for controlled rollouts.}
            \resumeItem{Persisted models with rich \textbf{metadata}: training counts, evaluation metrics, dataset checksums, and reference feature statistics to support \textbf{reproducibility} and \textbf{drift} awareness when loading trusted artifacts only.}
            \resumeItem{Enforced engineering rigor with \textbf{pytest} and coverage thresholds, \textbf{Ruff} and \textbf{mypy}, \textbf{pre-commit}, container-friendly packaging, and operational guides for \textbf{load testing} and \textbf{Grafana} monitoring.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{news-api} $|$ \emph{TypeScript, Express, Node.js, Redis, OpenAPI, Docker, Kubernetes}}{}
          \resumeItemListStart
            \resumeItem{Implemented a \textbf{production-oriented} news search API on \textbf{Express} and \textbf{TypeScript} integrating the GNews provider with a \textbf{pluggable cache} (in-memory or \textbf{Redis}) to deduplicate identical queries and protect upstream quota.}
            \resumeItem{Hardened the edge: \textbf{Helmet} security headers, configurable \textbf{rate limiting}, optional \textbf{client API keys} on \texttt{/api/*}, \textbf{TRUST\_PROXY}-aware client IP handling, upstream \textbf{HTTP timeouts}, strict response validation, and \textbf{502} mapping for provider failures.}
            \resumeItem{Instrumented for operations: \textbf{Pino} JSON logs with \textbf{request IDs}, \texttt{/metrics} in \textbf{Prometheus} text format, optional \textbf{OpenTelemetry} export to OTLP, and Kubernetes-style \textbf{liveness} and \textbf{readiness} probes.}
            \resumeItem{Published an \textbf{OpenAPI} contract at \texttt{/openapi.yaml}; shipped a multi-stage, \textbf{non-root} Dockerfile with health checks, \textbf{docker-compose}, example \textbf{Kubernetes} manifests, and CI emphasizing audits, \textbf{SBOM}, and provenance-style supply-chain checks.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{StreamHive} $|$ \emph{Go, TCP/TLS, custom framing (SHV1), Prometheus, Docker}}{}
          \resumeItemListStart
            \resumeItem{Authored a \textbf{Go} library and CLI experimenting with \textbf{distributed, content-addressed} blob storage over \textbf{TCP}: length-prefixed \textbf{SHV1} frames, explicit wire \textbf{handshake version}, and context-aware listen/dial with \textbf{TLS} hooks and connection limits.}
            \resumeItem{Implemented an in-memory \textbf{BlobStore} behind a stable interface, separating transport and storage so future \textbf{replication} and \textbf{peer discovery} can evolve without rewriting the framing layer.}
            \resumeItem{Exposed standard \textbf{/livez}, \textbf{/readyz}, and \textbf{/metrics} HTTP endpoints alongside the TCP data plane for orchestrator-friendly deployments; documented public API \textbf{semver} and architecture trade-offs in \textbf{CHANGELOG} and design docs.}
            \resumeItem{Applied mature engineering workflow: \textbf{golangci-lint}, \textbf{Makefile} targets (test, race, coverage, vet), Docker image, and CI that \textbf{pins third-party Actions to SHAs}, uploads coverage, and emits a \textbf{CycloneDX SBOM}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, C, PHP, JavaScript/TypeScript, SQL, Java} \\
     \textbf{Frameworks}{: React, Vue.js, Express (Node.js), Django, Laravel, FastAPI, Symfony, Gin} \\
     \textbf{ML / NLP}{: scikit-learn, XGBoost; text features (TF--IDF, embedding models)} \\
     \textbf{Cloud / DevOps}{: Docker, Kubernetes, AWS, Terraform, Kafka, GitHub Actions, CI/CD, Prometheus, Grafana, OpenTelemetry} \\
     \textbf{Databases \& cache}{: PostgreSQL, MySQL, MariaDB, MongoDB, SQLite, Redis}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Algorithms Specialization (Stanford), Machine Learning (DeepLearning.AI), Meta Backend/Frontend Developer}}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Politecnico di Torino}{Sep 2025 -- Present}
    {M.Sc. in Computer Engineering}{Turin, Italy}
  \resumeSubheading
    {Politecnico di Torino}{Sep 2021 -- Sep 2025}
    {B.Sc. in Computer Engineering}{Turin, Italy}
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
    \small{English (Bilingual), Persian (Bilingual), German (Professional), Italian (Fluent), French (Fluent)}

\end{document}